---
title: "Regression Portfolio"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
output: html_document
---
##### This document holds different regression models I have learned throughout my various statistical courses!

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Multiple Linear Regression

```{r}
## Getting the data
hotelData <- read.csv(file.choose())
  
## Exploratory data analysis
plot(hotelData[2:6])
```
```{r}
round(cor(hotelData[2:6]), 2)
```

##### Addressing Multicollinearity
###### 1. Multicollinearity is defined as a condition where two or more predictors are highly correlated with one another. Consequences of multicollinearity can be the instability of coefficent estimates and an inaccurate estimate of the variance
###### 2. As you can see from the scatterplox matrix and the correlation table, there seems to be high correlation between Energy_cons and area as well as numrooms and area
###### 3. The good news is that multicollinearity does not prevent you from obtaining precise predictions, and since this is the aim of our model we can continue without much worry

```{r}

```

```{r}
## Developing a tentative model
model <- lm(Energy_cons ~ area + age + numrooms + OccRate, data=hotelData)
summary(model)
```



```{r}
## Residual Plot
plot(model, which=1)

```
```{r}
## QQ Plot
plot(model, which=2)
```








